---
title: 'Developing Data Products Course Porject: Economic Data Series Viewer Shiny App'
author: "Guang Yang"
date: "May 13, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Economic Data Series Viewer
* ###Overview
    + The shiny app "Economic Data Series Viewer" is an interactive tool to study economic data series from [FRED](https://fred.stlouisfed.org/)
    + Please click [here](https://gyang14.shinyapps.io/economicdataseriesview/) to enjoy the app.
    + Please feel free to dive into [the code of the app and the presentation on GitHub](https://github.com/GYang14/Data-Product-Course-Project-Shiny-Application-and-Reproducible-Pitch)
    + Please see slides 3-5 for more introduction of this app

## User Guide
1. Enter the series_id of the economic data series of your interest into box: **"Primary Economic Data Series"**

2. Enter the series_id of the economic data series that you want to compare with the primary series into box: **“Secondary Economic Data Series”**

3. Specify the time period of your interest in **"Interested Time Window"**

4. Click the bottom **"Submit"** to see your result: time series chart on the right, scatterplot matrix with correlation at bottom

* ### Note: 
    + series_id sample: CPIAUCSL,DEXUSEU, SP500, DGS10, DTB3, and so on;
    + please see details of source data and full list of series_ids at [FRED](https://fred.stlouisfed.org/)

## Introduction to Economic Data Series_id

#### Series_id is the ID of economic data series on [FRED](https://fred.stlouisfed.org/). There are 470,000 US and international time series from 84 sources available. Following are some examples:

* CPIAUCSL: Consumer Price Index for All Urban Consumers: All Items

* DEXUSEU: U.S. / Euro Foreign Exchange Rate

* SP500: S&P 500©

* DGS10: 10-Year Treasury Constant Maturity Rate

* DTB3: 3-Month Treasury Bill: Secondary Market Rate 


## Sample Output

Part of the app output would be a time series chart. By default inputs, the server would generate a time series chart as the one generated by following code:
```{r echo=TRUE, message=FALSE}
library(quantmod)
    PD<-getSymbols("DTB3",src='FRED',auto.assign = FALSE)
    names(PD)<-"PD"
    SD<-getSymbols("DGS10",src='FRED',auto.assign = FALSE)
    names(SD)<-"SD"
    TimeWindow<-"2015/2017"
    PD<-PD[TimeWindow]
    Last<-SD[TimeWindow]
    name<-paste("top chart:","DTB3","; bottom chart:","DGS10")
    chartSeries(PD, line.type = "b",name=name, TA="addTA(Last,on=NA, type = 'b' )")
```

For more details about the app, please try it out at [here](https://gyang14.shinyapps.io/economicdataseriesview/)